Investigating magnetic dynamo evolution with TESS field dwarfs

### 2017-10-05 ms.tex
more small changes

\paragraph{Expected Impact}
Initially, we will provide rotation period posterior probability density
functions and best fit estimates for around 30,000 high priority FFI targets.
We will then produce a catalog of rotation periods for lower priority FFI
stars using a combination of Lomb-Scargle periodogram and autocorrelation
techniques.
Finally, we will release a catalog of rotation periods for all two-minute
cadence targets.
The full catalog will likely contain several million rotation periods.
We will release code for inferring stellar ages from rotation periods, based
on a new gyrochronology relation calibrated using \TESS\HERMES spectra, \Gaia\
kinematics and comoving pairs.
We will also release an open source python package for measuring rotation
periods of both FFI and two-minute cadence targets.

>>>>

\paragraph{Expected Impact}
We will provide rotation period posterior probability density functions and
best fit estimates for around 30,000 high priority FFI targets and a catalog
of rotation periods for lower priority FFI stars using a combination of
Lomb-Scargle periodogram and autocorrelation techniques.
Finally, we will release a catalog of rotation periods for all two-minute
cadence targets.
The full catalog will likely contain several million rotation periods.
We will release code for inferring stellar ages from rotation periods, based
on a new gyrochronology relation calibrated using \TESS\HERMES spectra, \Gaia\
kinematics and comoving pairs.
We will also release an open source python package for measuring rotation
periods of both FFI and two-minute cadence targets.
